Machine Learning rooted Potential piloted RRT* for expeditious Path Planning

### 2018-12-21 Research Paper/paper.tex
paper jaldi

\subsection{Ideal Path and Potential Constants:}
To find the ideal constants of potential field , we first found the ideal path by using BFS and Dijkstra and then reverse engineered our way to find the ideal potential functions for over 100,000 images

\begin{figure}
\begin{center}
\includegraphics[scale=1]{images2.png}
    \caption{The above image shows the ideal path to calculate the ideal path using BFS and Dijkstra.} \label{fig1}
\end{center}
\end{figure}

\subsection{Training:}
We took the centres of the each obstacle blob and the total area of the obstacles as the features and trained it with the potential using Random Forest Regressor model on around 100,000 images randomly generated images.

>>>>

\begin{figure}
\begin{center}
\includegraphics[scale=1.1]{merge_image(1).png}
    \caption{(a)The obstacle filled image. (b) The ideal path calculated using BFS and Dijkstra. (Section 3.2)} \label{fig1}
\end{center}
\end{figure}

\subsection{Ideal Path and Potential Constants:}
To find the ideal constants of potential field , we first found the ideal path by using BFS and Dijkstra and then reverse engineered our way to find the ideal potential functions for over 100,000 images. An example is shown in the figure above.

\subsection{Training:}
The position of the obstacle is an important determinant of the RRT* Tree. So is the area of the obstacle. So we took the centres of the each obstacle blob and the total area of the obstacles as the features and trained it with the potential using Random Forest Regressor model on around 100,000 images randomly generated images. We then used the potential funtion thus predicted to run an RRT* APF tree and an example is shown in Fig. 3.
\vspace{10mm}
\begin{figure}
\begin{center}
\includegraphics[scale=1.5]{img_bam.png}
    \caption{ The tree growth and piloted sampling of the nodes in RRT-Star with APF for the trained value of Potential Function. The tree converges directly to the destination and provides a very good approximation of the shortest path.} \label{fig1}
\end{center}
\end{figure}
\begin{figure}
\begin{center}
\includegraphics[scale=1.5]{tree.png}
    \caption{ The tree growth of RRT-Star with APF for a non-ideal value of Potential Function. It is evident that repulsion from the obstacle is not significant enough and that there is unnecessary branching of the tree. The final path is not a good approximation of the shortest path.} \label{fig1}
\end{center}
\end{figure}
\begin{figure}
\begin{center}
\includegraphics[scale=0.65]{stuck.png}
    \caption{ An illustration of a case where the tree gets stuck in a local minimum, due to highly unsuitable value of Potential Function.}\label{fig1}
\end{center}
\end{figure}
